\LARGE \bf Eye-Tracking: a New Look at Human-Robot Interaction Assessment

### 2014-10-02 paper.tex
updated procedure
fixed the introduction- no fix me

\fixme{organize/rewrite this paragraph}

\fixme{Mention skin conductance as well}

Evaluation of HRI is mostly done through qualitative questionnaires and
qualitative data (interaction videos, interviews for example). The physiological
measurements such as eye tracking being precise, pertinent and portable at the
same time provides an added value to the researcher.  However, this needs to be
complemented with the qualitative data as well.

Eye-tracking data is of high temporal precision as
compared to some of the physiological data sources such as fMRI or other
biometric devices used to measure the palpitation and the body temperature. The
eye tracking devices are portable enough as opposed to the bulky apparatus used
in fMRI~\cite{rosenthal2013neural}.  Eye tracking data provides more direct
access to the users' attention than other portable and physiological data
sources such as EEG; this makes eye-tracking data a pertinent source to measure
attention.

@@

\subsubsection{Apparatus}
\begin{enumerate}
\item Stationary
\item Mobile 
\item Dual eye-tracking

@@

Upon their arrival at the experiment site, the participants signed a
consent form and answered a small questionnaire about demographics and
participant's experience with educational robots (this we later consider
as expertise). The participants were placed in front of the playground
(Figure~\ref{expe}) and were equipped with the SMI eye-tracking glasses. The
actual experiment consisted in two phases: observation phase and
interaction phase.

>>>>

Evaluation of HRI is mostly done through qualitative questionnaires and
qualitative data (interaction videos, interviews for example). The physiological
measurements such as eye tracking being precise, pertinent and portable at the
same time provides an added value to the researcher.  Eye-tracking data is of high temporal precision as compared to some of the physiological data sources such as fMRI or other
biometric devices used to measure the palpitation and the body temperature. The
eye tracking devices are portable enough as opposed to the bulky apparatus used
in fMRI~\cite{rosenthal2013neural}.  Eye tracking data provides more direct
access to the users' attention than other portable and physiological data
sources such as EEG and wristbands measuring skin conductance and pulse rate; this makes eye-tracking data a pertinent source to measure
attention.

@@

\subsubsection{Apparatus}

\fixme{tell about the spatial and temporal resolution of different eye-trackers}

\begin{enumerate}
\item Stationary
\item Mobile 
\item Dual eye-tracking

@@

Upon their arrival at the experiment site, the participants signed a
consent form and answered a small questionnaire about demographics and
participant's experience with educational robots (this we later consider
as expertise). The participants were placed in front of the playground
(Figure~\ref{expe}) and were equipped with the SMI eye-tracking glasses. The eye-tracker records the gaze data at 30Hz with an accuracy of 0.5 degrees at 40 centimetres distance; and the scene camera of the eye-tracking glasses records the video in HD.  The
actual experiment consisted in two phases: observation phase and
interaction phase.
